---
title: "Data Format"
author: "Steve Brooks"
date: "August 2, 2015"
output: html_document
---
# Model Factors
Important factors for energy management include:

* Data Interval
* Date Period
* Intervention
  * Behvaior Based
  * Custom Projects


# Performance Periods
Use a indicator variables to designate the start and end of baseline and performance periods.

```{r, echo=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
load("~/R/sem/data/prod_temp.rda")
```
```{r}
start <- prod_temp%>%attr("action_item_start")
performance <- prod_temp%>%attr("performance_start")
pt_period <-prod_temp%>%
  mutate(.baseline = ifelse(date < start, TRUE, FALSE),
         .performance = ifelse(date > performance, TRUE, FALSE))

pt_period%>%
  head()%>%
  knitr::kable()
```

# Calculating the start and end of each period
The start and end of each period can be calculated from the table

```{r}
pt_period%>%
  tidyr::gather(period, active,.baseline:.performance)%>%
  filter(active)%>%
  group_by(period)%>%
  summarise(start = min(date),
            end = max(date))%>%
  knitr::kable()
```

# Weather Data
Weather files - wx
