---
title: "Lead/Lag Dataframes"
author: "Steve Brooks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(lubridate)
library(sem)
df <- data.frame(days = floor_date(now(), "day") + days(1:5),
                 var1 = 2:6,
                 var2 = rnorm(5))
```

## Lead/Lag
Production, processing, can take longer than the data interval.  For example, daily data for a process with a three-day processing time.  The daily input or output influences energy consumption on days before (output) or after (input).  The `lag_df` and `lead_df` functions are utilities for easily leading or lagging the dataframe.  

- __Lag__ the dataframe.  Suitable for _input_ production variables when the processing period is longer than the data interval.
- __Lead__ the dataframe.  Suitable for _output_ production variables when the processing period is longer than the data interval.


### Lag

#### Basic

```{r}
df%>%lag_df(days)%>%
  knitr::kable()
```

#### Depth of delay

The `nrows` variable sets the depth of the lag or lead.  The default sets nrows to 1.

```{r}
lag_df(df, days, nrows = 2)%>%
  knitr::kable()
```

#### Append
By default, the lagged or lead columns are appended to the orginial dataframe.  Just the lagged or lead column can be returned by setting append to FALSE.

```{r}
lag_df(df, days, append = FALSE)%>%
  knitr::kable()
```


### Lead

```{r}
df%>%lead_df(days)%>%
  knitr::kable()
```


