---
title: "Diagnostics"
author: "Steve Brooks"
date: "August 3, 2015"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(broom)
library(ggplot2)
library(lubridate)
library(nlme)
library(sem)

load("~/R/sem/data/pt_period.rda")
load("~/R/sem/data/milk.rda")
load("~/R/sem/data/wx_KPSC.rda")

pt_join <- pt_period%>%
  dplyr::inner_join(wx_KPSC)

```
Energy models need to be checked for autocorrelation and consistency over production and temperature variables.
Fit a model predicting Energy with Tave and Production as the predictor 
```{r}
lm <- pt_period%>%
  lm(energy ~ t_ave + prod, data = .)

lm%>%glance()%>%knitr::kable()
```

# Residuals
## Autocorrelation of residuals
## Error Assumptions - normally distributed

```{r}
lm_df <- lm%>%
  augment()

lm_df%>%
  dplyr::select(.resid)%>%
  mutate(.resid_lag = lag(.resid))%>%
  na.omit()%>%
  ggplot2::ggplot(aes(x = .resid, y = .resid_lag))+
  geom_point(alpha = 0.1)
  
```

The model displays significant auto-correlation.  

### Lag Term
One option was to include the lagging production term.  Adding the lag production term does not reduce autocorrelation

```{r}
lm <- pt_period%>%
  mutate(lag_prod = lag(prod),
         lag2_prod = lag(lag_prod),
         lead_prod = lead(prod),
         lag_temp = lag(t_ave))%>%
  lm(energy ~ t_ave + lag_temp + prod + lag_prod + lag2_prod + lead_prod, data = .)

lm_df <- lm%>%
  augment()

lm_df%>%
  dplyr::select(.resid)%>%
  mutate(.resid_lag = lag(.resid))%>%
  na.omit()%>%
  ggplot2::ggplot(aes(x = .resid, y = .resid_lag))+
  geom_point(alpha = 0.1)
```


### Weekly Model
A weekly model __improves__ the model by __increasing__ the r-squared and __reducing__ the autocorrelation of the residuals.

```{r}
lm <- pt_period%>%
  mutate(wk_yr = paste(week(date), "-", year(date)))%>%
  group_by(wk_yr)%>%
  dplyr::summarise_each(funs(sum), -date, -.baseline, -.performance)%>%
  mutate(lag_prod = lag(prod))%>%
  lm(energy ~ t_ave + prod + lag_prod, data = .)

lm%>%
  glance()%>%
  knitr::kable()

lm_df <- lm%>%
  augment()

lm_df%>%
  dplyr::select(.resid)%>%
  mutate(.resid_lag = lag(.resid))%>%
  na.omit()%>%
  ggplot2::ggplot(aes(x = .resid, y = .resid_lag))+
  geom_point(alpha = 0.1)
```


## Model 2
Model 2 

```{r}
milk%>%
  filter(.baseline)%>%
  do(broom::augment(lm(energy ~ . - date, data = .)))%>%
  mutate(.resid_lag = lag(.resid))%>% # Check Autocorrelation of the Residuals
  ggplot2::ggplot(aes(x = .resid, y = .resid_lag))+
  geom_point(alpha = 0.2)

```

## Checking Model Errors (residual)

```{r}
model <- pt_join%>%
  filter(.baseline)%>%
  lm(energy ~ CDD_30 + prod, data = .)%>%
  augment()

# Energy vs. Residuals + Fitted Line
model%>%
  ggplot(aes(x = energy, y = .resid))+
  geom_point(alpha = 0.1)+
  geom_smooth()+
  theme_light()

# Production vs. Residuals + Fitted line
model%>%
  ggplot(aes(x = prod, y = .resid))+
  geom_point(alpha = 0.1)+
  geom_smooth()+
  theme_light()

# Production vs. Residuals + Fitted line
model%>%
  ggplot(aes(x = CDD_30, y = .resid))+
  geom_point(alpha = 0.1)+
  geom_smooth()+
  theme_light()
```

# Generalized Least Squares



```{r}
glmod <- tac_ww%>%
  mutate(nobs = dplyr::row_number(date))%>%
  na.omit()%>%
  gls(energy ~ influent, correlation = corAR1(form = ~ nobs),
             data = .)
```

